### 2024-09-19 documentation/supplement.tex
Stephan's edits for Article + Supplement

\subsection{Miscellaneous tips}
\begin{itemize}
    \item Shield the beam as soon as alignment of a particular section is done. This increases safety, and avoids accidentally bumping into aligned components.
    \item \textit{Walking the beam}: Any beam can be threaded through two irises using two mirrors. The first mirror the beam meets is sometimes called the ``position'' mirror as it affects primarily the position of the beam. The second ``angle'' mirror instead primarily affects the angle. Assigning each mirror a separate function (position versus angle) and by adjusting them iteratively, is a good rule of thumb for driving the beam through the 2 irises and eventually hitting a specific point at the desired angle \cite{Thorlabs}. 
    \item Be mindful of reflections from all surfaces. Put back-reflecting component at a slight angle to the beam (e.g. the half wave plate) to avoid back-reflections directly into the laser. The back-reflection can then be caught with an iris placed in front of the laser.
    \item Make sure the beam is at the same height across the table. This can be done with an iris and an IR card. 
    \item Take extra care for directing the beam through the center of all lenses and active optical components.
\end{itemize}

\subsection{Parts and bill-of-materials}
All custom metal pieces are parts of the CAD assembly of the microscope. Ours were manufactured from aluminium stock in the university machine shop, but other materials are possible. Aluminium has the added benefit of anodization, which can help control stray light. For example, if the microscope was used in a Virtual Reality system, we would anodize the collection optics to reduce scattering from the projector's light.\newline
An overview of the microscope's cost is shown in Tab.~\ref{tab_costs}. Keep in mind that these prices can significantly change over time, while some products can become unobtainable and need to be replaced with a different or newer model.
%
\begin{table}
\begin{center}
  \begin{tabular}{ l c r } \hline
   \textbf{Item} & \textbf{Info} & \textbf{Cost} \\ \hline
\rowcolor{gray!20} 920 nm fs-pulsed Laser  & Spark Alcor 920 + Warranty & 90 k \\
                   ScanImage DAQ-System \& optimized PC & Vidrio & 20 k \\
\rowcolor{gray!20} Piezo collar & Physik Instrumente & 16 k	\\
            $2\times$ PMTs + preamplifiers  & Hamamatsu \& Thorlabs & 12 k \\
\rowcolor{gray!20} Pockels cell             & Conoptics &	11 k \\
                   Objective                & Nikon &  8 k \\
\rowcolor{gray!20} Machining custom parts   & Machine Shop; as per CAD files &  7 k \\
                   Optical filters          & AVR optics \& Semrock &  7 k \\
\rowcolor{gray!20} Lenses + optomechanics   & Thorlabs \& Newport &  7 k \\
                   Galvo-Resonant Scanner set & Novanta &  6 k \\
\rowcolor{gray!20} Electronics/cables/tools & Newark \& McMaster &  5 k \\
                   Mounting rack            & Emcor Enclosures &  3 k \\
\rowcolor{gray!20} Laser shutter            & Uniblitz/Vincent &  2 k \\
                   Laser safety goggles     & Edmund Optics &  1 k \\
\rowcolor{gray!20} Laser power meter        & Coherent &  1 k \\
                   Agarose \& fluorescent beads     & Thermofisher &  1 k \\
  \hline
 \textbf{Total}                    & & \textbf{197 k} \\
  \hline
  \end{tabular}
\end{center}
\caption{\textbf{Overview of the approximate cost in 2024-US\$} Note that this list excludes the optical table, and any other infrastructure costs such as compressors for air, and associated power supplies. This is just a summary. The detailed bill-of-materials is provided in the git repository.}\label{tab_costs}
\end{table}

\subsection{Structure and use of this document}
In the following sections, we will cover the setup and alignment of the microscope. This is split into three parts. The first part covers all components on the optical table that serve to condition the beam. The second part focuses on the  95 mm vertical post that holds the scanning mirror and scan lens assemblies. The third part is the microscope head with the attached collection optics. We will begin with the assembly on the optical table.\newline

Before building your own microscope, read these instructions fully. Check the CAD files, and make sure that the instructions make sense. This document follows closely our own alignment procedure, and we have done our best to be accurate. However, use common sense and do not follow these instructions blindly. Like all open instrumentation (under CC-BY-4.0), this work is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY, to the extent permitted by law; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.

\section{Assembly on the optical table}
%
\subsection{Beam conditioning}
An overview of the system for beam conditioning is shown in Fig.~\ref{sfig1} with key items labelled by capital letters. The following lines will cover the items, and their alignment.
%
\begin{figure}[!t]
    \includegraphics[width=\textwidth]{sfig1.jpg}
    \caption{{\bf Overall view of the beam conditioning path on the optical table.} Shown is a photograph of the components used to condition the beam for our microscope. Key components of the system are labelled with capital letters. The laser is shown as a red transparent line with intensity color coded. The beamsplitter cube (component D) splits the beam into two, halving its power. The Pockels cell (component G) reduces the power further. The reflections out of the Pockels cell and from the shutter (item J) are shown in yellow. The telescope (item K) magnifies the beam $\times 2$. All parts are explained in the text together with a note on their alignment.}
    \label{sfig1}
\end{figure}
%
\begin{enumerate}[]
    \item \textbf{A)} Laser beam coming out of the laser.

@@

    \item \textbf{I)} Si Switchable Gain Detector, 350 - 1100 nm (PDA36A2, Thorlabs). This is used to measure the light transmission through the Pockels cell, by monitoring scattered light from the beam block (H), that comes from the shutter back reflection. Make sure that the gain on the detector is chosen reasonably for laser power and ambient light level. In our system, a gain of 50 dB works well. If the ambient room light is too bright, a SM1-mounted infrared long-pass filter in front of the photodiode can help (e.g. FELH0850, Thorlabs). The goal of setting the gain is well-defined sigmoidal control curve in ScanImage: Light transmission through the Pockels cell starts at a minimum, and increases as the Pockels control voltage increases.

    \item \textbf{J)} 6 mm Shutter (LS6S2ZM1, Vincent Associates) connected to driver (VCM-D1, Vincent Associates) for control of the shutter during imaging. To check that the shutter is properly aligned leave it open and make sure that the beam is not clipped. When closed, the back-reflection has to be terminated in a beam block. This back-reflection combined with a physically close detector (Items H and I above) is used to calibrate the Pockels cell in ScanImage (see below).

    \item \textbf{K)} $2\times$ Beam Expander ($2\times$ Achromatic Galilean Beam Expander, GBE02-B, Thorlabs, inside SM1RC, Thorlabs). This expands the beam sufficiently to fill the apertures of the subsequent optics. Aligning the beam expander requires two steps. First, it has to be aligned to the optical axis. Second, it is critical that the beam stays collimated after the beam expander. For the first alignment, we use two irises, one screwed in the front, and one (on a reasonably long SM1 extension tube) behind the expander. The beam expander has to be positioned such that the irises cut into the beam symmetrically. Then, the expander is on-axis. Next, we need to adjust the collimation of the beam so that the beam is the same size at the exit and after a long distance using several mirrors, see Fig.~\ref{sfig3}. For optimal alignment, adjust the dial on the beam expander until it no convergence or divergence is visible.
    %
    \begin{SCfigure}
        \includegraphics[width=.5\textwidth]{sfig3.jpg}
      \caption{{\bf Method for making sure the beam is collimated.} Using a set of mirrors, the beam (yellow line) can be reflected back and fourth to increase the distance travelled. Along this path (in this example of $\approx 2.5\text{ m}$), the beam must not change size ($<1\text{ mm}$). This is validated with an IR detection card and switching between the forward and return path of the beam. This method allows to control beam divergence after the $2\times$ telescope to below 1 mrad.}
      \label{sfig3}
    \end{SCfigure}
    %
\item \textbf{L)} Iris (SM1D12C inside CP08, both Thorlabs) used to check alignment.

@@

\end{enumerate} 
%
When finished aligning the beam through all the optical components listed above, clamp them down on the table securely. Then shield the beam path with additional SM1 and SM2 tubing to increase safety and to protect the aligned optical components.
%
\subsection{Assembly of the scanning post}

@@

Following beam conditioning on the optical table, the beam is reflected up from the optical table towards the ceiling into a box housing the scanning mirrors. This is shown in Fig.~\ref{sfig4}A,B. Following the scanning mirrors, the beam travels up through the scan lens, and directed to the microscope head with another mirror.
%
\begin{figure}[h]
    \includegraphics[width=\textwidth]{sfig4.jpg}
    \caption{{\bf Overall view of the scanning post.} \textbf{A)} Side few. Key components of the system are labelled with capital letters. These are explained in the text together with a note on how to align these components. Importantly, the machined block (C) houses the scanning mirrors, and the scan lens assembly is placed in the SM2 house labelled (E). \textbf{B)} Frontal view. The PMT preamplifiers (component G) and the scanning mirror power supply (component H) are visible.}
    \label{sfig4}
\end{figure}
%
%
\begin{enumerate}[]
    \item \textbf{A)} Mirror (BPF10-03-P0, inside KCB1, with CP12 attached) - turn the beam at a right angle.
    \item \textbf{B)} Broadband filter (WG11010-B, Thorlabs, inside SM1L20 and SM1S20) - filter to keep dust out of the box housing the scanning mirrors.
    \item \textbf{C)} An aluminium box containing the resonant and slow galvanometer set (CRS8K/6215H Galvo Set, Novanta), mounted to 95 mm rail (XT95RC4, Thorlabs). A detailed description is provided below.
    \item \textbf{D)} Empty tubing.
    \item \textbf{E)} Scan lens - See detailed description below.
    \item \textbf{F)} Mirror in its housing (PF20-03-P01 and KCB2, both Thorlabs). While we used a round 2 inch mirror, this should be replaced with an elliptical mirror and housing (PFE20-P01 and KCB2EC, both Thorlabs). This increases the field-of-view because the cross-section of an ellipse at 45 degrees is a circle. At low magnification, a round mirror will lead to vignetting.
    \item \textbf{G)} PMT preamplifier (TIA60, Thorlabs) attached to a 95 mm rail.
    \item \textbf{H)} Power supply for the scanning mirrors (part of the Novanta scanning mirror set) housed in an electronics prototype box.
\end{enumerate}

@@

\begin{itemize}
    \item First, mount the 95 mm rail to the table. Then attach a bracket to the side to hold the scan lens (component D in Fig.~\ref{sfig3}), and one on top with a cage system to hold a mirror (component F in Fig.~\ref{sfig3}). For alignment with cage systems, we use a cage system alignment plate (VRC4CPT, Thorlabs). The rest of the assembly here will be done without any lenses. The goal is a well-aligned beam that travels through the center of all parts, and parallel to the optomechanical surfaces.
    \item The box housing the scanning mirrors is connected, trough SM1 tubing, to a mirror (component A in Fig.~\ref{sfig3}). To align this upper periscope mirror with the lower periscope mirror, mounted on the table, connect a piece of SM1 tubing to the upper mirror facing down, and  a second piece of SM1 tubing to the table mirror facing up (component M in Fig.~\ref{sfig1}) facing up. These two pieces meet in the air. Sliding a finger across the small gap between the two pieces makes misalignment easy to notice haptically. Mount the box housing the scanning mirrors such that you can not feel the transition from the lower SM1 tubing to the upper SM1 tubing.
    \item Next, we adjust the mirror (component A in Fig.~\ref{sfig4}A) so that light travels through the center of the scanning mirrors and up the 95 mm rail. This is done with irises. One is attached at the entry port of the scanning mirror box, e.g. in the SM1 tube (component B in Fig.~\ref{sfig4}A). Another two irises are attached, as far away as possible, to a 95 mm rail bracket. It is convenient to use the future holder of the scan lens (component D/E in Fig.~\ref{sfig4}). This ensures that the beam will pass through the center of the scan lens. As the mirror (component F in Fig.~\ref{sfig4}) is not installed yet, an IR detection card can conveniently be taped to the ceiling to make sure that the beam is on-axis. Of note, the resonant scanner is at its origin point when no power is being provided, but the slow galvanometer needs to be provided 0 Volt to position the mirror at its origin point. This can be done through the voltage supply, or to a good approximation through ScanImage by setting the scan mode to the highest possible zoom level. In our microscope design, it can be helpful to wiggle the lid to which the scanning mirrors are mounted (item C in Fig.~\ref{sfig4}). This step is tricky and can require some patience. 
    \item When confirmed that the light travels parallel to the 95 mm rail, we attach the mirror (component F in Fig.~\ref{sfig4}), and slide it along the cage rods to a position where the beam is reflected centrally through the caging system and the mount positioned on top of the 95 mm rail. This is done using the same set of two SM2-mounted irises that we used to make sure that light leaves the scanning mirror box without x or y displacement. The beam is now ready to travel through the microscope head.
\end{itemize}

\subsection{Assembly of the microscope head}
%
A picture is shown in Fig.~\ref{sfig5}.
\subsubsection{Components}
%
\begin{figure}[t!]
    \includegraphics[width=\textwidth]{sfig5.jpg}
    \caption{{\bf Overall view of the microscope head.} Key components of the system are labelled with capital letters. These are explained in the text together with a note on how to align these components.}
    \label{sfig5}
\end{figure}
%
\begin{enumerate}[]
    \item \textbf{A)} Empty tube, shielding the bream aligned in the previous section.
    \item \textbf{B)} Protected silver Mirror (PF30-03-P01, Thorlabs) inside KS3 and clamped down with XE25CL2 and another clamp. This mirror directs the beam through the tube lens. We will refer to this part as ``big mirror''. This is the first mirror that we will have to align.
    \item \textbf{C)} Tube lens - See detailed description below.
    \item \textbf{D)} Empty, just a tube used for spacing because the distance between the scan lens, tube lens, and objective is important.
    \item \textbf{E)} Tube holder (LCP01, Thorlabs) - just there to hold the lens straight, use with ER series 6 mm rods (ER6-P4, Thorlabs).
    \item \textbf{F)} Elliptical mirror (PFE20-P01 inside KCB2EC, both Thorlabs). We will refer to this part as ``collection mirror''. This is the second mirror that we will align.
\end{enumerate}
%
%
\subsubsection{Setup and alignment}

@@

\subsubsection{PMT installation}
PMTs are light sensitive. Always store them with their aperture covered with blackout tape when not in use (AT205-1.0 black aluminium foil tape, Thorlabs). When removing the tape for installation, this installation into the collection box must be done in darkness and as quickly as possible. We recommend to use black silicone putty (V-tie self setting silicone rubber), and have it ready for use to seal the gap between the PMTs and the aluminium box. Switch the room lights off, wait a few minutes to adapt to the darkness then mount the PMTs on their respective ports.

\subsection{Shield the light path}
Now that your microscope is ready, finish shielding the light path with SM1 and SM2 tubing, and cover the optical table with sheet metal. We use bent aluminium sheet, placed on small columns made from T-slotted rail.

@@

    \item Finally, use a fluorescent bead sample to measure the microscope's point spread function (PSF), see Fig.~\ref{sfig7}C. This will reveal more subtle misalignments or aberrations in the optics. We use a mix of 5000:1 100 nm fluorescent beads (``Dragon Green'' 480/520 from Bangs Laboratories) in in 1\% Agarose. To prepare this sample, take the beads from the fridge, vortex the container, take the 10 \textmu l and 49.5 g of water. Then microwave the mix with 0.5 g of Agarose until the solution is clear. While warm, place a drop on a microscope slide, and cover with a coverslip. Bring your sample to the microscope, and record a z-stack. Use low laser power to not damage the bead, or saturate the PMTs. The example shown was recorded with 5\% laser power at 99.9 zoom for 40 z-slices with 0.5 \textmu m spacing. The PSF profile should be symmetric, and a faint, but also symmetric, Airy ring visible around the bead, around 5 \textmu m away from center of the bead (see Fig. 2D in the main manuscript).

@@

    \caption{{\bf Assembly of the collection optics.} \textbf{A)} The assembled collection optics with bottom cover removed, perspective from below. \textbf{B)} The collection optics during the assembly process, similar to panel A. Key components are labelled (see text).}

@@

    \item \textbf{G)} With the condensers in place, we can install the optical band-pass filters in front of them. First the 525 nm band-pass filter (Semrock Brightline FF01-525/45-32, AVR Optics) for the green channel, which is secured with a nylon set screw (stainless steel nylon-tip set screw, 4-40 thread, 1/8in long). Orientation is important: The arrow is facing outwards, i.e. away from the inside of the box and towards the PMT along the light path.

@@

    \item \textbf{I)} Next, we attach the dichroic mirror that splits red and green light (Semrock Brightline FF562-Di03-40X52, AVR Optics) to its metal holder. The caret points towards the metal holder, such that the side the caret is pointing to contacts the metal when it is glued in place. When the glue has set, the mirror casing is screwed in place using stainless steel socket head screw, 4-40 Thread Size, 5/16 inches long.

@@

    \item \textbf{L)} PMT plate. The PMT attaches to the FLAT side of the PMT plates. The other side has a shallow cut out for the screw head to sit. The plate with the PMT attached screws into the rest of the assembly using 4-40 5/16 inch, socket cap screws.

@@

        \item Type in a name like \texttt{Y-galvo}

>>>>

\subsection{Miscellaneous tips}
\begin{itemize}
    \item Shield the beam as soon as alignment of a particular section is done. This increases safety, and avoids accidentally bumping into aligned components.
    \item \textit{Walking the beam}: Any beam can be aligned through two irises using two mirrors. The first mirror the beam meets is sometimes called the ``position'' mirror as it affects primarily the position of the beam. The second ``angle'' mirror instead primarily affects the angle. Assigning each mirror a separate function (position versus angle) and by adjusting them iteratively, is a good rule of thumb for driving the beam through the 2 irises and eventually hitting a specific point at the desired angle \cite{Thorlabs}. 
    \item Be mindful of reflections from all surfaces. Put back-reflecting component at a slight angle to the beam (e.g. the half wave plate) to avoid back-reflections directly into the laser. The back-reflection can then be caught with an iris placed in front of the laser.
    \item Make sure the beam is at the same height across the table. This can be done with an iris and an IR card. 
    \item Take extra care for directing the beam through the center of all lenses and active optical components.
\end{itemize}

\subsection{Parts and bill-of-materials}
All custom metal pieces are parts of the CAD assembly of the microscope. Ours were manufactured from aluminium stock in the university machine shop. Aluminium has the added benefit of anodization, which can help control scattered light. An overview of the microscope's cost is shown in Tab.~\ref{tab_costs}. Keep in mind that these prices can significantly change over time, while some products can become unobtainable and need to be replaced with a different or newer model.
%
\begin{table}
\begin{center}
  \begin{tabular}{ l c r } \hline
   \textbf{Item} & \textbf{Info} & \textbf{Cost} \\ \hline
\rowcolor{gray!20} 920 nm fs-pulsed Laser  & Spark Alcor 920 + Warranty & 90 k \\
                   ScanImage DAQ-System \& optimized PC & MBF Bioscience& 20 k \\
\rowcolor{gray!20} Piezo collar & Physik Instrumente & 16 k	\\
            $2\times$ PMTs + preamplifiers  & Hamamatsu \& Thorlabs & 12 k \\
\rowcolor{gray!20} Pockels cell             & Conoptics &	11 k \\
                   Objective                & Nikon &  8 k \\
\rowcolor{gray!20} Machining custom parts   & Machine Shop; as per CAD files &  7 k \\
                   Optical filters          & AVR optics \& Semrock &  7 k \\
\rowcolor{gray!20} Lenses + optomechanics   & Thorlabs \& Newport &  7 k \\
                   Galvo-Resonant Scanner set & Novanta &  6 k \\
\rowcolor{gray!20} Electronics/cables/tools & Newark \& McMaster &  5 k \\
                   Mounting rack            & Emcor Enclosures &  3 k \\
\rowcolor{gray!20} Laser shutter            & Uniblitz/Vincent &  2 k \\
                   Laser safety goggles     & Edmund Optics &  1 k \\
\rowcolor{gray!20} Laser power meter        & Coherent &  1 k \\
                   Agarose \& fluorescent beads     & Thermofisher &  1 k \\
  \hline
 \textbf{Total}                    & & \textbf{197 k} \\
  \hline
  \end{tabular}
\end{center}
\caption{\textbf{Overview of the approximate cost in 2024-US\$} Note that this list excludes the optical table, and any other infrastructure costs such as compressors for air, and associated power supplies. This is just a summary. The detailed bill-of-materials is provided in the git repository.}\label{tab_costs}
\end{table}

\subsection{Structure and use of this document}
In the following sections, we will cover the setup and alignment of the microscope. This is split into three parts. The first part covers all components on the optical table that serve to condition the beam. The second part focuses on the  95 mm vertical post that holds the scanning mirror and scan lens assemblies. The third part is the microscope head with the attached collection optics. We will begin with the assembly on the optical table. All along, we assume the reader will have downloaded and opened the CAD model as we will rely heavily on it.\newline
Before building your own microscope, read these instructions fully. Check the CAD files, and make sure that the instructions make sense. This document follows closely our own alignment procedure, and we have done our best to be accurate. However, use common sense and do not follow these instructions blindly. Like all open instrumentation (under CC-BY-4.0), this work is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY, to the extent permitted by law; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. Further, prior to the construction, check carefully the instruction manual of the scanning mirrors, photomultiplier tubes (PMTs), power supplies, Pockels cell, ScanImage, the Piezoelectric objective collar, and the filter mounting instructions.

\section{Assembly on the optical table}
%
\subsection{Beam conditioning}
An overview of the system for beam conditioning is shown in Fig.~\ref{sfig1} with key items labelled by capital letters. The following lines will cover the items, and their alignment.
%
\begin{figure}[!t]
    \includegraphics[width=\textwidth]{sfig1.jpg}
    \caption{{\bf Overall view of the beam conditioning path on the optical table.} Shown is a photograph of the components used to condition the beam for our microscope. Key components of the system are labelled with capital letters. The laser is shown as a red transparent line with intensity color coded. The beamsplitter cube (component D) splits the beam into two, halving its power. The Pockels cell (component G) reduces the power further. The reflections out of the Pockels cell and from the shutter (item J) are shown in yellow. The telescope (item K) magnifies the beam $\times 2$. The empty SM1 tube is an anodized aluminum SM1 lens tube cover (SC600, Thorlabs). All parts are explained in the text together with a note on their alignment.}
    \label{sfig1}
\end{figure}
%
\begin{enumerate}[]
    \item \textbf{A)} Laser beam coming out of the laser.

@@

    \item \textbf{I)} Si Switchable Gain Detector, 350 - 1100 nm (PDA36A2, Thorlabs). This is used for the laser power calibration  of the light transmitted through the Pockels cell.  The detector is facing the beam block (H) and monitors the light that comes from the shutter back reflection when closed. Make sure that the gain on the detector is chosen reasonably for laser power and ambient light level. In our system, a gain of 50 dB works well. If the ambient room light is too bright, a SM1-mounted infrared long-pass filter in front of the photodiode can help (e.g. FELH0850, Thorlabs). The goal of setting the gain is well-defined sigmoidal control curve in ScanImage: Light transmission through the Pockels cell starts at a minimum, and increases as the Pockels control voltage increases.

    \item \textbf{J)} 6 mm Shutter (LS6S2ZM1, Vincent Associates) connected to driver (VCM-D1, Vincent Associates) for control of the shutter during imaging. To check that the shutter is properly aligned leave it open and make sure that the beam is not clipped. When closed, the back-reflection is sent to a beam block. For this reason the shutter is not mounted exactly perpendicular to the incident beam but at a slight angle.

    \item \textbf{K)} $2\times$ Beam expander ($2\times$ Achromatic Galilean Beam Expander, GBE02-B, Thorlabs, inside SM1RC, Thorlabs). Aligning the beam expander requires two steps. First, it has to be aligned on the beam axis. Second, the beam needs to remain collimated after the beam expander, which is achieved by tuning the expander collar. For the first alignment, we use two irises, one screwed in the front, and one (on a reasonably long SM1 extension tube) behind the expander. The beam expander has to be positioned such that the beam travels through both iris, and such that the irises cut into the beam symmetrically. Next, we need to adjust the collimation of the beam using the expander collimation collar. It needs to be tuned so that the beam is the same size at the exit and after a long distance using several mirrors, see Fig.~\ref{sfig3}. 
    %
    \begin{SCfigure}
        \includegraphics[width=.5\textwidth]{sfig3.jpg}
      \caption{{\bf Method for making sure the beam is collimated.} Using a set of mirrors, the beam (yellow line) can be reflected back and fourth to increase the distance travelled. Along this path (in this example of $\approx 2.5\text{ m}$), the beam must not change size ($<1\text{ mm}$). This is validated with an IR detection card and switching between the forward and return path of the beam. This method allows to control beam divergence after the $2\times$ telescope to below 1 mrad.}
      \label{sfig3}
    \end{SCfigure}
    %
\item \textbf{L)} Iris (SM1D12C mounted on a CP08 plate, both Thorlabs) used to check alignment.

@@

\end{enumerate} 
%
When finished aligning the beam through all the optical components listed above, clamp them down on the table securely. Then shield the beam path with additional SM1 and SM2 tubing, and tubing cover (e.g. Thorlabs SC600, SM1 Anodized Aluminum Lens Tube Cover) to increase safety and to protect the aligned optical components.
%
\subsection{Assembly of the scanning post}

@@

Following beam conditioning on the optical table, the beam is reflected up from the optical table towards the ceiling into a box housing the scanning mirrors. This is shown in Fig.~\ref{sfig4}A,B. Following the scanning mirrors, the beam travels up through the scan lens, and directed to the microscope head with another mirror.
%
\begin{figure}[h]
    \includegraphics[width=\textwidth]{sfig4.jpg}
    \caption{{\bf Overall view of the scanning post.} \textbf{A)} Side few. Key components of the system are labelled with capital letters. These are explained in the text together with a note on how to align these components. Importantly, the machined block (C) houses the scanning mirrors, and the scan lens assembly is placed in the SM2 house labelled (E). \textbf{B)} Frontal view. The PMT preamplifiers (component G) and the scanning mirror power supply (component H) are visible.}
    \label{sfig4}
\end{figure}
%
%
\begin{enumerate}[]
    \item \textbf{A)} Mirror (BPF10-03-P0, inside KCB1, with CP12 attached) - turn the beam at a right angle.
    \item \textbf{B)} Broadband filter (WG11010-B, Thorlabs, inside SM1L20 and SM1S20) - filter to keep dust out of the box housing the scanning mirrors.
    \item \textbf{C)} An aluminium box containing the resonant and slow galvanometer set (CRS8K/6215H Resonant-Galvo Set, Novanta), mounted to 95 mm rail (XT95RC4, Thorlabs). A detailed description is provided below.
    \item \textbf{D)} Empty tubing (SM2V05, adjustable SM2 Lens Tube, Thorlabs).
    \item \textbf{E)} Scan lens - See detailed description below.
    \item \textbf{F)} Mirror in its housing (PF20-03-P01 and KCB2, both Thorlabs). While we used a round 2 inch mirror, this could be replaced with an elliptical mirror and housing (PFE20-P01 and KCB2EC, both Thorlabs). This would increase the field-of-view because the cross-section of an ellipse at 45 degrees is a circle. At low magnification, a round mirror will lead to vignetting.
    \item \textbf{G)} PMT preamplifier (TIA60, Thorlabs) attached to a 95 mm rail.
    \item \textbf{H)} Power supply for the scanning mirrors (part of the Novanta scanning mirror set) housed in an electronics prototype box.
\end{enumerate}

@@

\begin{itemize}
    \item First, mount the 95 mm rail to the table. Then attach a bracket (all from the XT95 series, Thorlabs) to the side to hold the scan lens (component D in Fig.~\ref{sfig3}), and one on top with a cage system to hold a mirror (component F in Fig.~\ref{sfig3}). For alignment with cage systems, we use a cage system alignment plate (VRC4CPT, Thorlabs). The rest of the assembly here will be done without any lenses. The goal is a well-aligned beam that travels through the center of all parts, and parallel to the optomechanical surfaces.
    \item The box housing the scanning mirrors is connected, trough SM1 tubing, to a mirror (component A in Fig.~\ref{sfig3}). To align this upper periscope mirror with the lower periscope mirror, mounted on the table, connect a piece of SM1 tubing to the upper mirror facing down, and  a second piece of SM1 tubing to the table mirror facing up (component M in Fig.~\ref{sfig1}) facing up. These two pieces meet in mid-air. The gap in between can be reduced to zero using adjustable length SM1 lens tube (e.g. SM1V10, Thorlabs, not shown in CAD) and can be further closed by a small portion of  lens tube cover (SC600, Thorlabs). 
    \item Next, we adjust the mirror (component A in Fig.~\ref{sfig4}A) so that light travels through the center of the scanning mirrors and up the 95 mm rail. This is done with irises. One is attached at the entry port of the scanning mirror box, e.g. in the SM1 tube (component B in Fig.~\ref{sfig4}A). Another two irises are attached, as far away as possible, to a 95 mm rail bracket. It is convenient to use the future holder of the scan lens (component D/E in Fig.~\ref{sfig4}). This ensures that the beam will pass through the center of the scan lens. As the mirror (component F in Fig.~\ref{sfig4}) is not installed yet, an IR detection card can conveniently be taped to the ceiling to make sure that the beam is on-axis. Of note, the resonant scanner is at its origin point when no power is being provided, but the slow galvanometer needs to be provided 0 Volt to position the mirror at its origin point. This can be done through the voltage supply, or to a good approximation through ScanImage by setting the scan mode to the highest possible zoom level. In our microscope design, it can be helpful to wiggle the lid to which the scanning mirrors are mounted (item C in Fig.~\ref{sfig4}). This step is tricky and can require some patience. 
    \item When confirmed that the light travels parallel to the 95 mm rail, we attach the mirror (component F in Fig.~\ref{sfig4}), and slide it along the cage rods to a position where the beam is reflected centrally through the caging system and the mount positioned on top of the 95 mm rail. This is done using the same set of two SM2-mounted irises that we used to make sure that light leaves the scanning mirror box without x or y displacement. The beam is now ready to travel through the microscope head.
\end{itemize}

\subsection{Assembly of the microscope head}
%
A picture is shown in Fig.~\ref{sfig5}.
\subsubsection{Components}
%
\begin{figure}[t!]
    \includegraphics[width=\textwidth]{sfig5.jpg}
    \caption{{\bf Overall view of the microscope head.} Key components of the system are labelled with capital letters. These are explained in the text together with a note on how to align these components.}
    \label{sfig5}
\end{figure}
%
\begin{enumerate}[]
    \item \textbf{A)} Empty tube, shielding the beam aligned in the previous section.
    \item \textbf{B)} Protected silver Mirror (PF30-03-P01, Thorlabs) inside KS3 and clamped down with XE25CL2 and another clamp. This mirror directs the beam through the tube lens. We will refer to this part as ``big mirror''. This is the first mirror that we will have to align.
    \item \textbf{C)} Tube lens - See detailed description below.
    \item \textbf{D)} Empty, just a tube used for spacing because the distance between the scan lens, tube lens, and objective is important.
    \item \textbf{E)} Tube holder (LCP01, Thorlabs) - just there to hold the lens straight, use with ER series 6 mm rods (ER6-P4, Thorlabs).
    \item \textbf{F)} Elliptical mirror (PFE20-P01 inside KCB2EC, both Thorlabs). We will refer to this part as ``collection mirror''. This is the second mirror that we will align.
\end{enumerate}
%
%
\subsubsection{Setup and alignment}

@@

\subsubsection{PMT installation}
PMTs are light sensitive. Always store them with their aperture covered with blackout tape when not in use (AT205-1.0 black aluminium foil tape, Thorlabs). When removing the tape for installation, this installation into the collection box must be done in darkness and as quickly as possible. We recommend to use black silicone putty (V-tie self setting silicone rubber), and have it ready for use to seal the gap between the PMTs and the aluminium box. Switch the room lights off, wait a few minutes to adapt to the darkness then mount the PMTs on their respective ports. Of note, when ordering the PMTs from Hamamatsu, one can request PMTs with particularly low dark count to reduce noise.

\subsection{Shield the light path}
Now that your microscope is ready, finish shielding the light path with SM1 and SM2 tubing, lens tube cover (SC600, Thorlabs), and cover the optical table with sheet metal. We use bent 1 mm aluminium sheet, placed on small columns made from T-slotted rail.

@@

    \item Finally, use a fluorescent bead sample to measure the microscope's point spread function (PSF), see Fig.~\ref{sfig7}C. This will reveal more subtle misalignment and aberration in the optics. We use a mix of 5000:1 100 nm fluorescent beads (``Dragon Green'' 480/520 from Bangs Laboratories) in in 1\% Agarose. To prepare this sample, take the beads from the fridge, vortex the container, take the 10 \textmu l and 49.5 g of water. Then microwave the mix with 0.5 g of Agarose until the solution is clear. While warm, place a drop on a microscope slide, and cover with a coverslip. Bring your sample to the microscope, and record a z-stack. Use low laser power to not damage the bead, or saturate the PMTs. The example shown was recorded with 5\% laser power at 99.9 zoom for 40 z-slices with 0.5 \textmu m spacing. The PSF profile should be symmetric, and a faint, but also symmetric, Airy ring visible around the bead, around 5 \textmu m away from center of the bead (see Fig. 2D in the main manuscript).

@@

    \caption{{\bf Assembly of the collection optics.} \textbf{A)} The assembled collection optics with bottom cover removed, perspective from below. \textbf{B)} The collection optics during the assembly process, similar to panel A. Key components are labelled (see text). EDITS TO MAKE IN THE ARROWS}

@@

    \item \textbf{G)} With the condensers in place, we can install the optical band-pass filters in front of them. First the 525 nm band-pass filter (Semrock Brightline FF01-525/45-32, AVR Optics) for the green channel, which is secured with a nylon set screw (stainless steel nylon-tip set screw, 4-40 thread, 1/8in long). Orientation is important: For this brand of filters, the arrow is following the light path, i.e. away from the inside of the box and towards the PMT.

@@

    \item \textbf{I)} Next, we attach the dichroic mirror that splits red and green light (Semrock Brightline FF562-Di03-40X52, AVR Optics) to its metal holder. The caret points towards the metal holder, such that the side the caret is pointing to contacts the metal when it is glued in place. When the glue has set, the mirror casing is screwed in place using stainless steel socket head screw, 4-40 Thread Size, 5/16 inches long. The glue used is a 5min non-sagging Epoxy. Three dichroic was attached with 3 points of glue of minimal volume.

@@

    \item \textbf{L)} PMT plate. The PMT attaches to the flat side of the PMT plates with 4 specialized low profile screws (CBSTSR2-6, Misumi). The other side has a shallow cut out for the screw head to sit. . The plate with the PMT attached screws into the rest of the assembly using 4-40 5/16 inch, socket cap screws.

@@

        \item Type in a name like \texttt{Y-Galvo}
